The value of intermediation -- results so far

### 2022-08-02 src/paper/paper.tex
Rearrange paper (proofs at the end)

\begin{proposition}
    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
\end{proposition}
\begin{proof}
    Monotonicity is evident. For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$. WLOG assume it is the latter, therefore $v(S_2) = 0$. As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
\end{proof}
In the following, let us assume that the assumptions required for monotonicity are always satisfied. It ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies: asymptotic value coincides with the axiomatic one using the uniform distribution for the latter. \textcolor{red}{Note: I realize that this paragraph is somewhat vague and needs explanation. However, for the current set of results, I do not rely on said theorem. If I end up using it later, I will expand on this part.}

Let $\varphi_P^n$ denote the Shapley-value of player $P$ in the case of $n$ players of type $A$. The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the platform does not converge to $f(1)$. This in turn implies that the aggregated Shapley-values of the fringe remain positive even in the limit.
\begin{proposition}
    \label{prop:one_sided}
    Let $f$ be continuous on [0, 1]. Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \varphi_p^n = \int_0^1 f(t) \dt .
    \end{align*}
\end{proposition}
\begin{proof}
    Let $R$ denote a permutation of the set of players ($N$). Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$. The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
    \begin{align*}
        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
    \end{align*}
    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$. Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition. More precisely, 
    \begin{align*}
        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
    \end{align*}
    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
    \begin{align*}
        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
    \end{align*}
    Putting all the above together, the value of player $P$ can be expressed as
    \begin{align*}
        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
    \end{align*}
    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
        &= \int_0^1 f(t) \dt .
    \end{align*}
\end{proof}

@@

\begin{corollary}
    The aggregated Shapley-value of the fringe is
    \begin{align*}
        \varphi_A^\infty = f(1) - \int_0^1 f(t) \dt.
    \end{align*}
    Furthermore, if $f$ is differentiable on $[0, 1]$, Then the value of the fringe can also be expressed as
    \begin{align*}
        \varphi_A^\infty = \int_0^1 t f'(t) \dt.
    \end{align*}
\end{corollary}
\begin{proof}
    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
    \begin{align*}
        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{A_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
    \end{align*}
    The second can be obtained by integration by parts:
    \begin{align*}
        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
    \end{align*}
\end{proof}

@@

\begin{corollary}
    $\varphi_P^\infty < f(1)$ and $\varphi_A^\infty > 0$ for any $f$ that is not constant.
\end{corollary}
\begin{proof}
    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$. The inequalities become strict if $f$ is not constant on the whole interval.
\end{proof}

@@

Getting back to the game at hand, let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively. Let $X_n$ be a random variable representing the number of players before $P$ when players are ordered according to the above procedure. Then, the probability of player $P$ having at most $k$ players of type $A$ before themselves is simply
\begin{align*}
    \Pr{X_n \leq k} = \prod_{j=k+1}^n \frac{j}{j + \lambda} .
\end{align*}
The following lemma establishes the continuous analogue of this statement.
\begin{lemma}
     As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$. Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
\end{lemma}
\begin{proof} \textcolor{red}{(Might have to fix sum indices)} \\
    The probability of $P$ having at most fraction $t$ of the other players before itself is
    \begin{align*}
        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
    \end{align*}
    Taking limits,
    \begin{align*}
        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    Let
    \begin{align*}
        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    By lemma \ref{lemma:log_convergence}, 
    \begin{align*}
        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
    \end{align*}
    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).

Finally, the weighted Shapley-value of player $i$ can be expressed as the expected marginal contribution of that player where the permutations are weighted according to the previous distribution.
\begin{proposition}
    \label{prop:one_sided_weighted}
    Let $f(t)$ be continuous on $[0, 1]$. Then
    \begin{align*}
        \varphi_P(\lambda, \infty) = \int_0^1 g(t) f(t) \dt
    \end{align*}
    where $g(t) = \lambda t^{\lambda - 1}$.
\end{proposition}
\begin{proof}
    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
    \begin{align*}
        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
    \end{align*}
    As before, using the fact that fringe players are identical, this can be rephrased as
    \begin{align*}
        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
        &= \E[f(X_n / n)]
    \end{align*}
    where $X_n$ is defined as above. $f$ is continuous, and therefore bounded on the compact set $[0, 1]$. As a consequence, $\frac{X_n}{n} \xrightarrow[]{\mathrm{d}} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 f(t) \mathrm{d}G(t) \\
        &= \int_0^1 g(t)f(t) \dt
    \end{align*}
    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
\end{proof}

\begin{corollary}
    $\varphi_P(\lambda, \infty)$ is increasing in $\lambda$ unless $f$ is constant.
\end{corollary}
\begin{proof}
    Let $X$ and $X'$ be random variables with cdfs $G_X = t^\lambda$ and $G_{X'}t^{\lambda'}$, respectively. For any $\lambda < \lambda'$, $t^\lambda > t^{\lambda'} \forall t \in [0, 1]$, meaning that $X'$ first-order stochastically dominates $X'$. As a result, for any monotonically increasing $f$,
    \begin{align*}
        \int_0^1 g_X(t)f(t) \dt = \E[f(X)] \leq \E[f(X')] = \int_0^1 g_{X'}(t)f(t)
    \end{align*}
    with strict inequality unless $f$ is constant almost everywhere. As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
\end{proof}

@@

\begin{corollary}
    If the weight of player $P$ goes to infinity (zero), its weighted Shapley value converges to $f(1)$ ($f(0)$).
\end{corollary}
\begin{proof}
    As $\lambda \to 0$, $X$ converges to the degenerate random variable $X_0$ for which $\Pr(X_0 = 0) = 1$. As a consequence, the expected value of $f(X)$ converges to $\E[f(X_0)] = f(0)$. $\lim_{\lambda \to \infty} \varphi^{\infty, \lambda}_P = f(1)$ can be shown along the same lines.
\end{proof}

@@

\begin{proposition}
    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
    \begin{align*}
        \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \dt .
    \end{align*}
\end{proposition}
\begin{proof}
    \label{prop:one_sided_multiple}
    First, let us rewrite the expected marginal contribution of player $P_i$ in the following way:
    \begin{align*}
        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_R v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R) \\
        &= \frac{1}{(n+m)!} \left[ \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] + \sum_{\{R | n_P(\mathcal{P}_{P_i}^R > 0)\}} \left[v(\mathcal{P}_{P_i}^R \cup \{i\}) - v(\mathcal{P}_{P_i}^R)\right] \right]
    \end{align*}
    Next, make use of the fact that the marginal contribution of a platform is zero if another platform is already present, and only depends on the number of fringe firms otherwise.
    \begin{align*}
        \varphi_{P_i}^{n, m} &= \frac{1}{(n+m)!} \sum_{\{R | n_P(\mathcal{P}_{P_i}^R = 0)\}} f (\mathcal{P}_{A}^R / n) \\
        &= \frac{1}{(n+m)!} \sum_{k=0}^n |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| f(k/n)
    \end{align*}
    Finally, notice that, while the permutations with $k$ fringe agents before $P_i$ does not depend on $k$, amongst those, the number of permutations with no platform before $P_i$ does depend on it. In particular,
    \begin{align*}
        |\{R | n_A(\mathcal{P}^R_{P_i} = k) \text{ and } n_P(\mathcal{P}^R_{P_i} = 0)\}| &= \frac{n!(n+m-k-1)!}{(n-k)!}
    \end{align*}
    and
    \begin{align*}
        \varphi_{P_i}^{n, m} &= \sum_{k=0}^n \frac{n!(n+m-k-1)!}{(n+m)!(n-k)!} f(k/n) \\
        &= \sum_{k=0}^n \frac{(n-k+1)(n-k+2) \dots (n-k+m-1)}{(n+1)(n+2) \dots (n+m)} f(k/n) \\
        &= \frac{1}{n+1}\sum_{k=0}^n \underbrace{\frac{(n(1-k/n)+1)(n(1-k/n)+2) \dots (n(1-k/n)+m-1)}{(n+2) \dots (n+m)} f(k/n)}_{S_n}
    \end{align*}
    For any $t = k/n \in [0, 1]$, 
    \begin{align*}
        S_n(t) \to (1-t)^{m-1}f(t) \equiv S(t).
    \end{align*}
    Furthermore, it is simple to verify that this convergence is uniform, and that $S_n$ and $S$ are all continuous functions. By Dini's theorem, the former properties imply that $S_n \xrightarrow[]{\mathrm{u}} S$ uniformly on $[0, 1]$.

@@

\begin{corollary}
    The per-unit Shapley-value of the fringe is
    \begin{align*}
        \varphi_A(k, \infty) = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
    \end{align*}
\end{corollary}
\begin{proof}
    The allocation is efficient for all $n \in \mathbb{N}$, therefore efficient in the limit, as well. The second equality can be obtained by integration by parts.
\end{proof}

@@

\begin{corollary}
    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$. $\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
\end{corollary}
\begin{proof} \textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
    $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$. As a consequence, $\varphi_A^{n, \infty}$ is also increasing in $m$ if $f'(t)$ is positive on some interval or, $f(t)$ is not constant. Conversely, $\varphi_{P}^{\infty, m} = 1 - \varphi_{A}^{\infty, m}$ is decreasing in $m$.
\end{proof}

@@

\textcolor{red}{\large No proofs or changes in this section. The next new results are in the appendix.}

@@

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions. Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$. Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.

\begin{lemma}
    \label{lemma:integral_convergence}
    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly. Then,
    \begin{align*}
        \lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) = \int_0^1 f(t) \dt.
    \end{align*}
\end{lemma}
\begin{proof}
    \begin{align*}
        &\lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) \\
        &= \lim_{n \to \infty} \frac{b-a}{n} \left[ \sum_{k=1}^n f \left( a + \frac{b-a}{n} \right) + \sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \right] \\
        &= \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left| f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right| \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right| \\
        &= \int_a^b f(t) \dt + (b-a) \underbrace{\lim_{n \to \infty} \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right|}_{=0 \text{ due to uniform convergence}} \\
        &= \int_a^b f(t) \dt
    \end{align*}
\end{proof}

@@

>>>>

\begin{proposition}
    \label{prop:monotone}
    The game $(N, v)$ is monotone and superadditive if and only if $f$ is increasing and $f(0) \geq 0$. % It is supermodular if and only if $f$ is convex.
\end{proposition}

In the following, let us assume that the assumptions required for monotonicity are always satisfied. It ensures that the games are of bounded variation, and thus the main theorem in \textcite{fogelman1980asymptotic} applies: asymptotic value coincides with the axiomatic one using the uniform distribution for the latter. \textcolor{red}{Note: I realize that this paragraph is somewhat vague and needs explanation. However, for the current set of results, I do not rely on said theorem. If I end up using it later, I will expand on this part.}

Let $\varphi_P^n$ denote the Shapley-value of player $P$ in the case of $n$ players of type $A$. The following proposition demonstrates the main idea of this paper: even as the number of fringe players goes to infinity, the Shapley-value of the platform does not converge to $f(1)$. This in turn implies that the aggregated Shapley-values of the fringe remain positive even in the limit.
\begin{proposition}
    \label{prop:one_sided}
    Let $f$ be continuous on [0, 1]. Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \varphi_p^n = \int_0^1 f(t) \dt .
    \end{align*}
\end{proposition}

@@

\begin{corollary}
    \label{cor:fringe_value}
    The aggregated Shapley-value of the fringe is
    \begin{align*}
        \varphi_A^\infty = f(1) - \int_0^1 f(t) \dt.
    \end{align*}
    Furthermore, if $f$ is differentiable on $[0, 1]$, Then the value of the fringe can also be expressed as
    \begin{align*}
        \varphi_A^\infty = \int_0^1 t f'(t) \dt.
    \end{align*}
\end{corollary}

@@

\begin{corollary}
    \label{cor:fringe_value_2}
    $\varphi_P^\infty < f(1)$ and $\varphi_A^\infty > 0$ for any $f$ that is not constant.
\end{corollary}

@@

Getting back to the game at hand, let the weights of players of type $A$ and $P$ be 1 and $\lambda$, respectively. Let $X_n$ be a random variable representing the number of players before $P$ when players are ordered according to the above procedure. Then, the probability of player $P$ having at most $k$ players of type $A$ before themselves is simply
\begin{align*}
    \Pr{X_n \leq k} = \prod_{j=k+1}^n \frac{j}{j + \lambda} .
\end{align*}
The following lemma establishes the continuous analogue of this statement.
\begin{lemma}
    \label{lem:entry_distr}
     As $n \to \infty$, $X_n \xrightarrow[]{\mathrm{d}} X$ with the cdf $G_X(t) = \lambda^t$. Consequently, the corresponding probability density function is $g(t) = \lambda t^{\lambda - 1}$.
\end{lemma}

Finally, the weighted Shapley-value of player $i$ can be expressed as the expected marginal contribution of that player where the permutations are weighted according to the previous distribution.
\begin{proposition}
    \label{prop:one_sided_weighted}
    Let $f(t)$ be continuous on $[0, 1]$. Then
    \begin{align*}
        \varphi_P(\lambda, \infty) = \int_0^1 g(t) f(t) \dt
    \end{align*}
    where $g(t) = \lambda t^{\lambda - 1}$.
\end{proposition}

\begin{corollary}
    \label{cor:platform_value_weighted}
    $\varphi_P(\lambda, \infty)$ is increasing in $\lambda$ unless $f$ is constant.
\end{corollary}

@@

\begin{corollary}
    \label{cor:paltform_value_weighted_2}
    If the weight of player $P$ goes to infinity (zero), its weighted Shapley value converges to $f(1)$ ($f(0)$).
\end{corollary}

@@

\begin{proposition}
    \label{prop:multiple_platforms}
    The limit of the Shapley-value (as $n \to \infty$) of each player of type $P$ is
    \begin{align*}
        \varphi_{P_i}^{\infty, m} = \int_0^1 (1-t) ^ {m-1} f(t) \dt .
    \end{align*}
\end{proposition}

@@

\begin{corollary}
    \label{cor:multiple_platforms}
    The per-unit Shapley-value of the fringe is
    \begin{align*}
        \varphi_A(k, \infty) = 1 - m\int_0^1 (1-t) ^ {m-1} f(t) \dt = \int_0^1 [1 - (1-t)^m] f'(t) \dt .
    \end{align*}
\end{corollary}

@@

\begin{corollary}
    \label{cor:multiple_platforms_2}
    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$. $\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
\end{corollary}

@@

@@

@@

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}[Proof of Lemma \ref{lemma:log_convergence}]
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions. Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$. Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.

\begin{lemma}
    \label{lemma:integral_convergence}
    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly. Then,
    \begin{align*}
        \lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) = \int_0^1 f(t) \dt.
    \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma \ref{lemma:integral_convergence}]
    \begin{align*}
        &\lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) \\
        &= \lim_{n \to \infty} \frac{b-a}{n} \left[ \sum_{k=1}^n f \left( a + \frac{b-a}{n} \right) + \sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \right] \\
        &= \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left| f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right| \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right| \\
        &= \int_a^b f(t) \dt + (b-a) \underbrace{\lim_{n \to \infty} \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right|}_{=0 \text{ due to uniform convergence}} \\
        &= \int_a^b f(t) \dt
    \end{align*}
\end{proof}

\section{Proofs of propositions and lemmas from the main text}

\begin{proof}[Proof of Proposition \ref{prop:monotone}]
    Monotonicity is evident. For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$. WLOG assume it is the latter, therefore $v(S_2) = 0$. As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:one_sided}]
    Let $R$ denote a permutation of the set of players ($N$). Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$. The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
    \begin{align*}
        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
    \end{align*}
    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$. Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition. More precisely, 
    \begin{align*}
        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
    \end{align*}
    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
    \begin{align*}
        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
    \end{align*}
    Putting all the above together, the value of player $P$ can be expressed as
    \begin{align*}
        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
    \end{align*}
    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$. Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
        &= \int_0^1 f(t) \dt .
    \end{align*}
\end{proof}

\begin{proof}[Proof of Corollary \ref{cor:fringe_value}]
    The first equality comes from the efficiency of the Shapley-value. The values of all players sum up to $f(1)$ for all $n \in \mathbb{N}$, therefore
    \begin{align*}
        \lim_{n \to \infty} \sum_{i=1}^n \varphi_{A_i}^n = \lim_{n \to \infty} (1 - \varphi_P^n ) = 1 - \int_0^1 f(t).
    \end{align*}
    The second can be obtained by integration by parts:
    \begin{align*}
        \int_0^1 t f'(t) \dt = tf(t) \mid_0^1 - \int_0^1 f(t) \dt = f(1) - \int_0^1 f(t) \dt
    \end{align*}
\end{proof}

\begin{proof}[Proof of Lemma \ref{lem:entry_distr}] \textcolor{red}{(Might have to fix sum indices)} \\
    The probability of $P$ having at most fraction $t$ of the other players before itself is
    \begin{align*}
        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
    \end{align*}
    Taking limits,
    \begin{align*}
        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    Let
    \begin{align*}
        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    By lemma \ref{lemma:log_convergence}, 
    \begin{align*}
        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
    \end{align*}
    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).

\begin{proof}[Proof of Corollary \ref{cor:fringe_value_2}]
    If $f$ is monotone increasing, then $f(0) \leq \int_0^1 f(t) \dt \leq f(1)$. The inequalities become strict if $f$ is not constant on the whole interval.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:one_sided_weighted}]
    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
    \begin{align*}
        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
    \end{align*}
    As before, using the fact that fringe players are identical, this can be rephrased as
    \begin{align*}
        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
        &= \E[f(X_n / n)]
    \end{align*}
    where $X_n$ is defined as above. $f$ is continuous, and therefore bounded on the compact set $[0, 1]$. As a consequence, $\frac{X_n}{n} \xrightarrow[]{\mathrm{d}} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 f(t) \mathrm{d}G(t) \\
        &= \int_0^1 g(t)f(t) \dt
    \end{align*}
    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
\end{proof}

\begin{proof}[Proof of Corollary \ref{cor:platform_value_weighted}]
    Let $X$ and $X'$ be random variables with cdfs $G_X = t^\lambda$ and $G_{X'}t^{\lambda'}$, respectively. For any $\lambda < \lambda'$, $t^\lambda > t^{\lambda'} \forall t \in [0, 1]$, meaning that $X'$ first-order stochastically dominates $X'$. As a result, for any monotonically increasing $f$,
    \begin{align*}
        \int_0^1 g_X(t)f(t) \dt = \E[f(X)] \leq \E[f(X')] = \int_0^1 g_{X'}(t)f(t)
    \end{align*}
    with strict inequality unless $f$ is constant almost everywhere. As $f$ is continuous, the latter is equivalent to $f$ being constant on the whole $[0, 1]$ interval.
\end{proof}

\begin{proof}[Proof of Corollary \ref{cor:paltform_value_weighted_2}]
    As $\lambda \to 0$, $X$ converges to the degenerate random variable $X_0$ for which $\Pr(X_0 = 0) = 1$. As a consequence, the expected value of $f(X)$ converges to $\E[f(X_0)] = f(0)$. $\lim_{\lambda \to \infty} \varphi^{\infty, \lambda}_P = f(1)$ can be shown along the same lines.
\end{proof}
